---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# history

[![Travis build status](https://travis-ci.org/or-house-vis/history.svg?branch=master)](https://travis-ci.org/or-house-vis/history)
 
history provides historical data on the Oregon State Legislature.

Currently it contains a chronological list of the House of Representatives based on the list on *Chronological List of Oregon Representatives from 1841 to Present* on the [Chief Clerk's Office website](https://www.oregonlegislature.gov/chief-clerk/Pages/representatives.aspx).

If you aren't an R user you may still find the data in [`chronology-patched.csv`](/data-raw/chronology-patched.csv) useful.

## Installation

You can install developement version of history with:
``` r
# install.packages("devtools")
devtools::install_github("history")
```

## House Representatives

A historical list of the representatives in the Oregon State House of Representatives is in `house_reps`:
```{r example}
library(history)
house_reps
```

The data comes from the [*Chronological List of Oregon Representatives from 1841 to Present*](https://www.oregonlegislature.gov/chief-clerk/Pages/representatives.aspx).  You can see when the data in this package was retrieved with:
```{r}
attr(house_reps, "retrieved")
```

The data parsing steps can be found in [`/data-raw`](/data-raw), in particular the data in the package in CSV form can be found in [`chronology-patched.csv`](/data-raw/chronology-patched.csv).

Some patches are made to the data, you can see the changes in the [`data-raw/README.md`](/data-raw/README.md).