# Patch House of Representatives chronology

Input `data-raw/chronology-clean.csv`

Output `data-raw/chronology-patched.csv` and `housereps.rda`

```{r setup}
library(tidyverse)
library(here)
```

```{r}
reps <- read_csv(here("data-raw", "chronology-clean.csv"))
```

## Rijken, Max

Rijken, Max missing in 1975 but listed in Chronological List of Oregon's Legislatures by Cecil L. Edwards, Senate Historian, published by the Legislative Administration Committee, 1993. 

```{r}
max_rijken <- data_frame(Legislator = "Rijken, Max",
    District = 38,
    Party = "D",
    Residence = "Newport, Benton, Lane, Lincoln",
    Gender = "Male",
    session_name = "1975 Session",
    session_year = 1975,
    regular = TRUE
    ) 
reps <- reps %>% 
  bind_rows(max_rijken)
```

## 1965 Roberts, Betty R.
```{r}
betty_roberts <- data_frame(Legislator = "Roberts, Betty R.",
    District = 6,
    Party = "D",
    Residence = "Portland, Multnomah",
    Gender = "Female",
    session_name = "1965 Session",
    session_year = 1965,
    regular = TRUE) 
reps <- reps %>%   
  bind_rows(betty_roberts)
```

## Jones, Benjamin F.

1909 Jones, Benjamin F. Independence, Polk 12 F? **This seems to be an error**

Should be Republican according to Chronological List of Oregon's Legislatures by Cecil L. Edwards, Senate Historian, published by the Legislative Administration Committee, 1993. 

```{r}
# Fix one party affilation
reps[reps$Legislator == "Jones, Benjamin F.", "Party"] <- "R"
```


## Grant, A. S.

```{r}
filter(reps, is.na(Gender))
```

```{r}
filter(reps, Legislator == "Grant, A. S.")
```

Assume male from later session:
```{r}
reps[reps$Legislator == "Grant, A. S.", "Gender"] <- "Male"
```

## Output


```{r}
reps <- reps %>% 
  arrange(session_year, regular, session_name, District) %>% 
  select(session_name, Legislator, District, everything())
```

```{r}
write_csv(reps, here("data-raw", "chronology-patched.csv"))
```

```{r}
retrieved <- 
  here("data-raw", "chronology-page.html") %>% 
  read_lines(n_max = 1) %>% 
  str_replace("<!-- Retrieved ", "") %>% 
  lubridate::ymd_hms()

attr(reps, "retrieved") <- retrieved

house_reps <- reps
usethis::use_data(house_reps)
```

