---
output: github_document
---

# Data scraping

## `house_reps`

The data `house_reps` is a minimally processed version of that on the [Chief Clerk's webpage](https://www.oregonlegislature.gov/chief-clerk).

To re-generate `house_reps`, run the scripts in order:

1. `01-scrape.Rmd`
2. `02-parse.Rmd`
3. `03-clean.Rmd`
4. `04-patch.Rmd` 

## `house_reps_regular`

`house_reps_regular` is a more processed data set that:

* only includes *Regular* sessions,
* after OR became a state, with
* legislators in the house at the **start** of the session, and 
* their party affiliation at the **start** of the session.

The code to generate `house_reps_regular` is in `05-regular.Rmd`.

## Patches 

To see the changes made by patches:
```{r setup, message=FALSE}
library(daff)
library(tidyverse)
library(here)
```


```{r}
clean_csv <- here("data-raw", "chronology-clean.csv")
patched_csv <- here("data-raw", "chronology-patched.csv")

# use same spec to read
spec <- spec_csv(clean_csv)

clean <- read_csv(clean_csv, col_types = spec)
patched <- read_csv(patched_csv, col_types = spec)

diffs <- diff_data(clean, patched, ordered = FALSE)
```

```{r, results='asis'}
diff_html <- render_diff(diffs, view = FALSE, fragment = TRUE,
  summary = TRUE)
writeLines(diff_html)
```

In interactive use, use this for full color view:
```{r, eval = FALSE}
render_diff(diffs)
```

